Appendix

### 2022-01-07 paper/manuscript/appendix.Rmd
add sep file for motor milestone attempt?

@@

## Tables 1&2 Motor Milestones Analysis Details

We examine whether the SAYcam participants' age of reaching particular developmental milestones (sitting, cruising, and walking) significantly influenced the proportion of hands or faces that they saw, using a mixed-effects regression with per-child random intercepts.

We tried including random slopes by age and milestone, but the models did not converge and/or were singular. Thus, for each milestone the R syntax was: \texttt{prop_faces ~ age * milestone + (1 | child_id)}.Children's age of achieving each milestone was dummy-coded (i.e., 0=milestone not reached; 1=milestone reached).

```{r, get-milestones, echo=F}
motor <- read_csv(here::here("data","raw_data", "saycam_walking_asq.csv"))
# A and S are sitting at 6mos
face_hand_by_age_milestones <- face_hand_by_age %>%
  mutate(sit = ifelse(child_id=="S" | child_id=="A", 1, 
                      ifelse(child_id=="Y" & age_day_bin > 8, 1, 0))) %>%
  mutate(cruise = ifelse((child_id=="S" & age_day_bin >= 9) | 
                      (child_id=="A" & age_day_bin >= 10) | 
                      (child_id=="Y" & age_day_bin > 9), 1, 0)) %>%
  mutate(walk = ifelse((child_id=="S" & age_day_bin > 10) |
                       (child_id=="A" & age_day_bin > 13) |
                       (child_id=="Y" & age_day_bin > 16), 1, 0)) %>%
  mutate(age = age_day_bin)

library(lmerTest)
# https://rpsychologist.com/r-guide-longitudinal-lme-lmer
# with random slopes and intercepts ((age_day_bin | child_id): is singular / not converging
# so we drop random slopes

face_all <- lmer(prop_faces ~ age * (sit + cruise + walk) + (1 | child_id), 
     data=face_hand_by_age_milestones) 
#summary(face_all) # cruise+ age:cruise-

hand_all <- lmer(prop_hands ~ age * (sit + cruise + walk) + (1 | child_id), 
     data=face_hand_by_age_milestones) 
#summary(hand_all) # cruise+ age:cruise-.

face_sit <- lmer(prop_faces ~ age * sit + (1 | child_id), 
     data=face_hand_by_age_milestones) 
hand_sit <- lmer(prop_hands ~ age * sit + (1 | child_id), 
     data=face_hand_by_age_milestones)

face_cruise <- lmer(prop_faces ~ age * cruise + (1 | child_id), 
     data=face_hand_by_age_milestones)
hand_cruise <- lmer(prop_hands ~ age * cruise + (1 | child_id), 
     data=face_hand_by_age_milestones)

face_walk <- lmer(prop_faces ~ age * walk + (1 | child_id), 
     data=face_hand_by_age_milestones)
hand_walk <- lmer(prop_hands ~ age * walk + (1 | child_id), 
     data=face_hand_by_age_milestones)
# make models compatible with stargazer
class(face_sit) <- "lmerMod"
class(hand_sit) <- "lmerMod"
class(face_cruise) <- "lmerMod"
class(hand_cruise) <- "lmerMod"
class(face_walk) <- "lmerMod"
class(hand_walk) <- "lmerMod"
```

### Sitting

Children's age at which they began sitting did not significantly predict changes in either the amount of faces or hands that they saw.

```{r, include=F, results='asis'}
#summary(face_sit) # ns
stargazer(face_sit, title="Predicting Faces by Ability to Sit", 
          header=F, dep.var.labels = "Proportion of Faces")

stargazer(face_sit, hand_sit)
```

```{r, include=F, results='asis'}
#summary(hand_sit) # ns
stargazer(hand_sit, title="Predicting Hands by Ability to Sit", 
          header=F, dep.var.labels = "Proportion of Hands")
```

```{r, results='asis'}
stargazer(face_sit, hand_sit, title="Change in Face and Hand Prevalence by Ability to Sit", 
          header=F, dep.var.labels = c("Proportion of Faces","Proportion of Hands"), nobs=F)
```

### Cruising

As children became able to cruise, they saw significantly more faces ($\beta = 0.27$) and hands ($\beta = 0.26$. 
For faces, there was a significant negative interaction of age and cruising ($\beta = -0.03$, $p=0.025$), and a marginal positive effect of age ($\beta = 0.03$, $p=0.055$).

```{r, include=F, results='asis'}
#summary(face_cruise) 
# age+., cruise+*, age*cruise-*
stargazer(face_cruise, title="Predicting Faces by Ability to Cruise", 
          header=F, dep.var.labels = "Proportion of Faces")
```

```{r, include=F}
f1 <- ggpredict(face_cruise, c("age", "cruise")) %>% plot(add.data=T) +
  xlim(5, 24) + ylim(0,1) + ggtitle("Predicted effect on faces seen") + 
  xlab("Age (months)") + ylab("Proportion of faces")

h1 <- ggpredict(hand_cruise, c("age", "cruise")) %>% plot(add.data=T) +
  xlim(5, 24) + ylim(0,1) + ggtitle("Predicted effect on hands seen") + 
  xlab("Age (months)") + ylab("Proportion of hands")

ggpubr::ggarrange(f1, h1, nrow=1, common.legend=T)
```

```{r, include=F, results='asis'}
#summary(hand_cruise) 
# cruise+*, age*cruise-.
stargazer(hand_cruise, title="Predicting Hands by Ability to Cruise", 
          header=F, dep.var.labels = "Proportion of Hands") 
```

```{r, results='asis'}
stargazer(face_cruise, hand_cruise, title="Change in Face and Hand Prevalence by Ability to Cruise", 
          header=F, dep.var.labels = c("Proportion of Faces","Proportion of Hands"), nobs=F)
```

### Walking

As children became able to walk, they saw marginally more hands ($\beta = 0.09$, $p=0.052$).

```{r, include=F, results='asis'}
#summary(face_walk) # ns
stargazer(face_walk, title="Predicting Faces by Ability to Walk", 
          header=F, dep.var.labels = "Proportion of Faces")
```

```{r, include=F, results='asis'}
#summary(hand_walk) # walk+.
stargazer(hand_walk, title="Predicting Hands by Ability to Walk", 
          header=F, dep.var.labels = "Proportion of Hands")
```

```{r, results='asis'}
stargazer(face_walk, hand_walk, title="Change in Face and Hand Prevalence by Ability to Walk", 
          header=F, dep.var.labels = c("Proportion of Faces","Proportion of Hands"), nobs=F)
```

>>>>

---
title: "Appendix"
author: "Bria Long"
date: "1/6/2022"
output: word_document
---

@@
